Iroko: Predictive Datacenter Congestion Control

### 2017-12-12 Documents/Report/eval.tex
Modify eval.tex to use selected qlen plot

To analyze the drop rate we measured the number of packets built up in the queue
on all switches for the same set of traffic patterns and plotted a cumulative
distribution graph (Figure \ref{fig:qlen}). A high queue size is considered to
be bad. We have fixed the maximum queue size to 50 packets.

>>>>

To analyze the drop rate we measured the number of packets built up in the queue
on all switches for the same set of traffic patterns and plotted a cumulative
distribution graph. In Figure \ref{fig:qlen} we are plotting some selected
graph. A high queue size is considered to be bad. We have fixed the maximum
queue size to 50 packets.
